\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}{: #2 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

% Modified command for projects with description right after name
\newcommand{\resumeProjectHeading}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} - \textit{#2} & #3 \\
    \end{tabular*}\vspace{-5pt}
}

% Modified command for work experience with role after company
\newcommand{\resumeWorkHeading}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} - \textit{#2} & #3 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{\Large Tejas Manoj Athalye}\\
  \small Pune, India $|$ \href{tel:+917666803812}{+91 7666803812} $|$ \href{mailto:me.tejasathalye@gmail.com}{me.tejasathalye@gmail.com}\\
  \small \href{https://tejas-athalye-portfolio.vercel.app/}{Portfolio} $|$ \href{https://github.com/LitZeus}{GitHub} $|$ \href{https://www.linkedin.com/in/tejasathalye/}{LinkedIn}
\end{center}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {NBN Sinhgad Technical Institutes Campus}{Pune, India}
    {Bachelors of Engineering in Computer Engineering; CGPA: 7.89}{2021 -- 2025}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
  \resumeWorkHeading
    {Cloud Computing \& Project Management Intern}{KasNet Technologies Pvt. Ltd.}
    {2023 -- 2024}
    \resumeItemListStart
      \resumeItem{Cloud Optimization}{Optimized Azure SQL, improving storage efficiency by 20\%.}
      \resumeItem{Data Visualization}{Developed Power BI dashboards, increasing data-driven efficiency by 30\%.}
      \resumeItem{Project Management}{Improved team collaboration by 15\% through Agile methodologies.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {Varicose Veins Detection Using YOLO}{AI-Powered Medical Diagnosis}
    {\href{https://github.com/LitZeus/detect-it}{GitHub}}
    \resumeItemListStart
      \resumeItem{Deep Learning Model}{Developed a YOLO-based classification system enhanced with EfficientNet.}
      \resumeItem{Dataset}{Curated 3,000+ images for training, improving detection accuracy.}
    \resumeItemListEnd

  \resumeProjectHeading
    {SwipeHire}{AI-Powered Job Matching App}
    {In Progress}
    \resumeItemListStart
      \resumeItem{Recommendation System}{Leverages resume analysis and engagement metrics for job matching.}
      \resumeItem{Bidirectional Swiping}{Allows recruiters and candidates to match efficiently.}
    \resumeItemListEnd

  \resumeProjectHeading
    {NFTix}{NFT-Based Ticketing Platform}
    {\href{https://github.com/LitZeus/NFTix}{GitHub}}
    \resumeItemListStart
      \resumeItem{Blockchain Security}{Uses Solidity and IPFS for fraud prevention.}
      \resumeItem{Smart Contracts}{Enables resale with royalties via smart contracts.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
\resumeSubHeadingListStart
  \item \textbf{Programming Languages:} Python, Solidity, Javascript.
  \item \textbf{Technologies:} SQL, MongoDB, Smart Contracts, Web3, Cloud Computing (Azure), MS Excel, Power BI, Power Query, Linux, Generative AI, LLM.
  \item \textbf{Frameworks \& Libraries:} NumPy, pandas, scikit-learn, PyTorch, Matplotlib, Seaborn, Ultralytics, MLflow, React, Vite, NextJS
  \item \textbf{Project Management \& Tools:} Agile Methodologies, Jira, MS Project
  \item \textbf{DevOps:} Docker, Kubernetes, CI/CD, Git, Github, Workflows
\resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------------
\section{Publications}
\resumeSubHeadingListStart
  \resumeItem{Detection of Varicose Veins Using YOLO}{Published in IARJSET, Vol. 11, Issue 10, 2024.\\
  \href{https://doi.org/10.17148/IARJSET.2024.111012}{DOI: 10.17148/IARJSET.2024.111012}}
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------------
\section{Certifications}
\vspace{-10pt}
\begin{multicols}{3}
\begin{itemize}[leftmargin=*, itemsep=2pt, parsep=0pt]
  \item \href{https://github.com/LitZeus/certificates/blob/main/Azure_certification.pdf}{Azure Fundamentals (AZ-900)}
  \item \href{https://github.com/LitZeus/certificates/blob/main/google-data-analytics-cert.pdf}{Google Data Analytics}
  \item \href{https://github.com/LitZeus/certificates/blob/main/google-advanced-data-analytics-cert.pdf}{Google Advanced Data Analytics}
  \item \href{https://github.com/LitZeus/certificates/blob/main/google-project-management-cert.pdf}{Google Project Management}
  \item \href{https://github.com/LitZeus/certificates/blob/main/Google%20Cybersecurity%20Professional%20Certificate.pdf}{Google Cybersecurity}
  \item \href{https://github.com/LitZeus/certificates/blob/main/google-business-intelligence-cert.pdf}{Google Business Intelligence}
\end{itemize}
\end{multicols}

%-----------EXTRACURRICULARS-----------------
%-----------EXTRACURRICULARS-----------------
\section{Extracurricular Activities}
\resumeSubHeadingListStart
  \resumeItem{Hackathon Achievement}{Winner of \$100 prize in ‘OKTO Track’ at UNFOLD 24, Bengaluru.}
  \resumeItem{FSAE Electric Racing}{Core member of STES Racing team for FSAE 2024; worked on powertrain and control logic.}
  \resumeItem{Sinhgad Capture Crew}{Photographer and media coordinator for institute-wide events under Sinhgad Technical Education Society.}
  \resumeItem{Event Leadership}{Led the Drone Flying Competition at Sinhgad National Springfest 2024.}
  \resumeItem{Sports}{2× National Games Participant and 2× State Gold Medalist in Karate (2018, 2019).}
\resumeSubHeadingListEnd


\end{document}